%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19) reworked on 2023 by Leonardo Pozzati
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Leonardo Pozzati (leon.pozzati@gmail.com)
% Based on a 
% Jan Vorisek (jan@vorisek.me) rework
% of a template by Jan Küster (info@jankuester.com)
% modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
%----------------------------------------------------------------------------------------


\usepackage{qrcode} % Required to generate QR code of the link to FontAwesome5 icons
\usepackage[pdfauthor={Leonardo Pozzati},
            pdftitle={Leonardo Pozzati - Resume},
            pdfsubject={This is the outstanding resume of Leonardo Pozzati},
            pdfcreator={pdflatex},
            hidelinks]{hyperref}

\definecolor{greenForName}{RGB}{0,140,69}         
\definecolor{ItalianRed}{RGB}{205, 33, 42}       
\definecolor{DutchBlue}{RGB}{0, 61, 165}           
\newcommand{\myHilight}[2]{\textit{\color{#1}{#2}}}


\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\,\huge\textcolor{green}{\textbf{\MakeUppercase{Leonardo}}}\normalfont\,}} % First name
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Pozzati}}}\normalfont}} % Last name
	
	\vspace{6pt}
	
	{\mbox{\textcolor{ItalianRed}{\textbf{\,\,\,Senior Software Engineer}}} \linebreak \textcolor{DutchBlue}{\textbf{{\,\,\,Embedded Systems}}}} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.30\textwidth} % 30% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{Home}{12}{\small\href{https://goo.gl/maps/fXe4xLSt1rT5tuoG6}{Hontenissestraat 45, Tilburg}}\\
    % In the third parameter, the text, there is an href to directly call the phone number and a flag of the country
    \icon{Phone}{6}{\small \href{tel:+393347108340}{\worldflag[width=2mm]{IT} \texttt{+39\,334\,710\,8340}}} \\
    \icon{Phone}{6}{\small \href{tel:+31629808909}{\worldflag[width=2mm]{NL} \texttt{+31\,6\,2980\,8909}}} \\
\end{minipage}
\begin{minipage}[t]{0.25\textwidth} % 25% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{Github}{8}{\href{https://github.com/vaeVict1s}{github}}\\
	\icon{Linkedin}{8}{\href{https://www.linkedin.com/in/leonardo-pozzati-4769471bb}{linkedIn}}\\
	\icon{At}{8}{\href{mailto:leon.pozzati@gmail.com}{email}}
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\cvsect{Who Am I?}

\begin{minipage}[t]{0.4\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\mbox{I am an Italian Senior Software Engineer,} 
	\linebreak
	\mbox{with a sound background in Mathematical Physics.}
	\mbox{I worked in several fields, before moving to}
	\linebreak
	\mbox{the Netherlands on 6th of April 2022.}
	\linebreak
	\mbox{I like to think of myself as a serious professional,}
	\linebreak
	\mbox{strongly driven and project oriented.}
	\linebreak
	\mbox{I have a lot to learn and I find interesting and challenging}
	\linebreak
	\mbox{to grow both with junior and more experienced Engineers,}
    \linebreak
    \mbox{being able to focus on solitary projects as well.}
	\linebreak
	\mbox{I've been told I could make outstanding presentations.}
	\linebreak
	\mbox{I am better in person though.}
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.5\textwidth} % 50% of the page for the skills bar chart
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\begin{barchart}{5.5}
		\baritem{\textbf{Bash}}{95}
		\baritem{\textbf{C / C++}}{90}
		\baritem{\textbf{Python}}{90}
		\baritem{\textbf{PhP/MySQL}}{65}
		\baritem{\textbf{Papyrus}}{80}
		\baritem{\textbf{Git}}{90}
		\baritem{\textbf{LaTeX}}{95}
	\end{barchart}
\end{minipage}

\begin{center}
	\bubbles{6/\textbf{Linux}, 5/\textbf{Windows}, 6/\textbf{Shell},  5/\textbf{IDEs}, 5/\textbf{Office}, 6/\textbf{SAFe}} %, 5/Office Suite}
\end{center}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
	\entry
		{2022 -- 2023}
		{Senior Software Engineer}
		{TOPIC Embedded Systems.}
		{\mbox{I was assigned to \textcolor{DutchBlue}{ASML} as part of a \myHilight{DutchBlue}{recently out-farmed team}; 
        my main contribution was}
        \linebreak 
        \mbox{helping the \myHilight{DutchBlue}{robustness} of the latter, 
        \myHilight{DutchBlue}{implementing, testing and integrating} modules,} 
        \linebreak 
        \mbox{\myHilight{DutchBlue}{implementing CICD} in the w.o.w. of the team 
        in collaboration with the local T\&I team} 
		\linebreak
		\mbox{and developing the \myHilight{DutchBlue}{design of a State Machine Framework}.} 
        \linebreak{}
        \texttt{C / C++}\slashsep\texttt{Python}\slashsep\texttt{Bash}\slashsep\texttt{CICD}\slashsep\texttt{UML and EA}\slashsep\texttt{SAFe}}

	\entry
	    {2018 -- 2021}
	    {Senior Software Engineer}
	    {ProMarket}
	    {\mbox{I worked for the \myHilight{DutchBlue}{fintech startup} ProMarket, 
        developing in Python and in C++ a \myHilight{DutchBlue}{networking}} 
        \linebreak 
        \mbox{\myHilight{DutchBlue}{framework} between the investment clients 
        and the strategy-computing servers}
        \linebreak{}
        \mbox{on top of the \myHilight{DutchBlue}{ZeroMq} library. 
        I also developed in Python a \myHilight{DutchBlue}{sentiment analysis engine}.}
        \linebreak{}
        \texttt{C / C++}\slashsep\texttt{Python}\slashsep\texttt{Bash}\slashsep\texttt{Networking}\slashsep\texttt{ZeroMQ}}

	\entry
		{2015 -- 2018} %\\\footnotesize{part time}}
		{Software Developer}
		{Eveilidia}
        {\mbox{I worked for Eveilidia, an IT company. My job was the 
        \myHilight{DutchBlue}{debugging and maintaining} of} 
        \linebreak  
        \mbox{web applications’ back-end running on Linux Fedora.}
        \linebreak{}
        \texttt{Python}\slashsep\texttt{Bash}\slashsep\texttt{Fedora Linux}\slashsep\texttt{Web Services}}

	\entry
		{2012 -- 2013\\\footnotesize{freelance}}
		{Developer and Tester}
		{Ubuntu Italian Community Forum}
        {\mbox{I proposed the \myHilight{DutchBlue}{idea} and took part in the 
        \myHilight{DutchBlue}{development} of a \myHilight{DutchBlue}{command line parser}, 
        a C version of}
        \linebreak{}
        \mbox{the Python \myHilight{DutchBlue}{argparse module}.} 
        \linebreak{}
        \mbox{It is available for \myHilight{DutchBlue}{free download and use} 
        on GitHub: \href{https://github.com/Vincenzo1968/myoptParser}{Vincenzo1968/myoptParser}}
        \linebreak{}
        \texttt{Python / C}\slashsep\texttt{Bash}\slashsep\texttt{FOSS}\slashsep\texttt{Remote Colab}}

	\entry
		{2006 -- open\\\footnotesize{part time}}
		{Owner}
		{Almalu Trastevere - Cocktail Bar}
		{My family started from scratch a business in entertainment, 
        mainly frequented by \mbox{English-speaking} customers. This gave me, moreover, 
        the opportunity of improving my language skills on a daily basis. 
        This business is still working and mainly managed by my older brother, 
        Alessio, who is managed by our mother.}

	\entry
		{2010 -- 2012} %\\\footnotesize}
		{PHP - MySQL Developer}
		{SirCup}
		{I worked for SirCup, a company which organizes sport 
        tournaments. I \myHilight{DutchBlue}{developed and maintained MySQL databases} 
        and relative \myHilight{DutchBlue}{data-handling and presentation PHP routines}, 
        specifically for their soccer tournaments.}
		% {\lorem\lorem\\ \texttt{PHP}\slashsep\texttt{Laravel}}

	\entry
	    { Miscellanea }
	    {}
	    {}
	    {\mbox{After I won a scholarship, I worked for a year as a \myHilight{DutchBlue}{librarian} 
        in Roma 3 University library.} \linebreak \mbox{I’ve been \myHilight{DutchBlue}{tutoring students} 
        in mathematics and physics for several years, preparing them for} 
        \linebreak 
        \mbox{any grade level, especially from high school to univeristy.}
        \linebreak{}
        \mbox{I worked for a couple of years at Chiostro del Bramante, 
        a museum in Roma, \myHilight{DutchBlue}{keeping watch on}} \linebreak \mbox{\myHilight{DutchBlue}{artworks} during exhibitions.}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{}
		{Master's Degree in Mathematical Physics - 110/110 cum Laude}
		{Universita' Roma Tre}
		{My research work investigates the \myHilight{DutchBlue}{relaxation to the equilibrium} of a 
        \myHilight{DutchBlue}{supersaturated gas} through a \myHilight{DutchBlue}{critical droplet} which triggers the phase transition into liquid.
        \newline 
        After writing down both a stochastical and a deterministic \myHilight{DutchBlue}{mathematical model} 
        of this \myHilight{DutchBlue}{metastable thermodynamic system}, 
        I wrote the C++ simulations, run them and carried out a massive data analysis in Python 
        finding out interesting results in the context of \myHilight{DutchBlue}{Non-Equilibrium Statistical Mechanics}.}
	\entry
		{}
		{Bachelor's Degree in Physics}
		{Universita' Roma Tre}
		{}
	\entry
		{}
		{High School}
		{Pio IX}
		{Humanities-focused Catholic highschool run by Benedictines Monks.}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.2\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Languages}
    
	\begin{tabular}{l r}
    \textbf{Italian} & \,native \\
	\textbf{English     } & \,C1\\
    \textbf{Dutch} & \,Self Studying

    \end{tabular}
\end{minipage}
\hfill
\begin{minipage}[t]{0.35\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\cvsect{Hobbies}
    
	I love Art, open air activities like horse riding and hicking, cooking and reading when home.
\end{minipage}
\hfill
\begin{minipage}[t]{0.35\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\cvsect{Non profit}
	
    I try to be a better version of me \linebreak every day, working in charities and \linebreak \mbox{being open mostly.} \linebreak
    % I am currently involved in the Linux group at Lochal in Tilburg.
\end{minipage}

\cvsect{Personal Projects}
\begin{entrylist}
    \entry{}
    {3D Scanner}
    {}
    {Along with the \myHilight{DutchBlue}{Open Source Lab at Lochal Library} in Tilburg, 
    I am building a 3D scanner based on the \myHilight{DutchBlue}{OpenScan} project.
    \newline{}
    The idea is to make this scanner available to people interested 
    in 3D printing to help them have fun with their projects.}
    \entry{}
    {Domotics and IoT}
    {}
    {I am assembling a \myHilight{DutchBlue}{modular home assitant}, both gathering what is already 
    available through \myHilight{DutchBlue}{open source communities} and developing functionalities myself.
    \newline
    This project started with a manager for the garden and the automation of an Ikea roller blind.
    \newline
    I am also assembling a \myHilight{DutchBlue}{drone} as the standalone hardware 
    for this assistant: the chassis is \myHilight{DutchBlue}{3D-printed} with the support of Lochal library,  
    prototype schematics and circuit board's layout are made with \myHilight{DutchBlue}{KiKad} 
    and the software runs on a \myHilight{DutchBlue}{Rasbperry Pi 4}.}    
    \entry{}
    {Chat Bot Training}
    {}
    {With the idea of \myHilight{DutchBlue}{training a chat bot on a specific domain}, 
    I am writing down a bibliography of milestones in Software Engineering 
    in order to feed the bot with them.
    \newline
    This project is in its early stage and \myHilight{DutchBlue}{its purpose is mostly educative}.}
\end{entrylist}

    

%----------------------------------------------------------------------------------------
\begin{minipage}[t]{0.5\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
\cvsect{Socials}

	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
    \qrcode[height=0.3in]{https://github.com/vaeVict1s}                           \quad \icon{Github}{10}{\href{https://github.com/vaeVict1s}{ \small github.com/vaeVict1s}}\\ \\
    
    
	\qrcode[height=0.3in]{https://www.linkedin.com/in/leonardo-pozzati-4769471bb} \quad \icon{Linkedin}{10}{\href{https://www.linkedin.com/in/leonardo-pozzati-4769471bb}{ \small in/leonardo-pozzati-4769471bb}}\\ \\


    \qrcode[height=0.3in]{mailto:leon.pozzati@gmail.com}                          \quad \icon{At}{10}{\href{mailto:leon.pozzati@gmail.com}{ \small leon.pozzati@gmail.com}}

\end{minipage}
\hfill
\end{document}
