%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
\usepackage{qrcode}
%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\huge\textcolor{green}{\textbf{\MakeUppercase{Leonardo}}}}} % First name
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Pozzati}}}}} % Last name
	
	\vspace{6pt}
	
	{\huge \mbox{\textcolor{red}{Senior Software Engineer}} \linebreak \textcolor{blue}{Embedded Systems}} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{Home}{8}{\small\href{https://goo.gl/maps/fXe4xLSt1rT5tuoG6}{Hontenissestraat 45, Tilburg}}\\
	\icon{Phone}{8}{\small +31 6 25112398}\\
	% \icon{At}{12}{\href{mailto:leon.pozzati@gmail.com}{Personal email}}\\	
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	% \icon{Globe}{12}{\href{https://alyx.vance.me}{alyx.vance.me}}\\
	\icon{Github}{8}{\href{https://github.com/vaeVict1s}{github}}\\
	\icon{Linkedin}{8}{\href{https://www.linkedin.com/in/leonardo-pozzati-4769471bb}{linkedIn}}\\
	\icon{At}{8}{\href{mailto:leon.pozzati@gmail.com}{email}}
	% \icon{Twitter}{12}{\href{https://twitter.com/@alyxvance}{@alyxvance}}\\
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\cvsect{Who Am I?}

\begin{minipage}[t]{0.4\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\mbox{I am an Italian Senior Software Engineer,} 
	\linebreak
	\mbox{with a sound background in Mathematical Physics.}
	\mbox{I worked on several fields, before moving to}
	\linebreak
	\mbox{the Netherlands on 6th of April 2022.}
	\linebreak
	\mbox{I would like to think at myself like a serious professional,}
	\linebreak
	\mbox{strongly driven and project oriented. Nevertheless, }
	\linebreak
	\mbox{I have lot to learn and I find interesting and challenging}
	\linebreak
	\mbox{to grow with junior Engineers along the way.}
	\linebreak
	\mbox{I've been told I could make outstanding presentations.}
	\linebreak
	\mbox{I am better in person though.}
	
	% \lorem \lorem \lorem \lorem \lorem\\ % Dummy text
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.5\textwidth} % 50% of the page for the skills bar chart
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\begin{barchart}{5.5}
		\baritem{Bash}{95}
		\baritem{C / C++}{90}
		\baritem{PhP/MySQL}{65}
		\baritem{Bootstrap}{70}
		\baritem{Git}{90}
		\baritem{LaTeX}{95}
	\end{barchart}
\end{minipage}

\begin{center}
	\bubbles{6/Linux, 5/Windows, 6/Shell,  4/IDEs, 5/Office Suite, 6/SAFe} %, 5/Office Suite}
\end{center}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
	\entry
		{2022 -- 2023}
		{Senior Software Engineer}
		{TOPIC Embedded Systems.}
		{\mbox{I was assigned to ASML as part of a recently out-farmed team; my main contribution was} \linebreak \mbox{helping the robustness of the latter, testing and integrating already developed modules,}  \linebreak \mbox{implementing CICD in the w.o.w. of the team in collaboration with local T\&I team} 
		\linebreak
		\mbox{and developing almost the whole design of a State Machine Framework.} \linebreak \texttt{C / C++}\slashsep\texttt{Python}\slashsep\texttt{Bash}\slashsep\texttt{CICD}\slashsep\texttt{UML and EA}\slashsep\texttt{SAFe}}
	\entry
	    {2018 -- 2021}
	    {Senior Software Engineer}
	    {ProMarket}
	    {\mbox{I worked for the fintech startup ProMarket, developing in Python and in C++ a networking} \linebreak \mbox{framework between the investment clients and the strategy-computing
servers} \linebreak \mbox{on top of the ZeroMq library. I also developed in Python a sentiment analysis engine.} \linebreak \texttt{C / C++}\slashsep\texttt{Python}\slashsep\texttt{Bash}\slashsep\texttt{Networking}\slashsep\texttt{ZeroMQ}}
	\entry
		{2015 -- 2018} %\\\footnotesize{part time}}
		{Software Developer}
		{Eveilidia}
        {\mbox{I worked for Eveilidia, an IT company. My job was the debugging and mantaining of} \linebreak  \mbox{web applications’ back-end
running on Linux Fedora.} \linebreak \texttt{Python}\slashsep\texttt{Bash}\slashsep\texttt{Fedora Linux}\slashsep\texttt{Web Services}}
	\entry
		{2012 -- 2013\\\footnotesize{freelance}}
		{Developer and Tester}
		{Ubuntu Italian Community Forum}
        {\mbox{I proposed the idea and took part in the development of a command line parser, a C version of} \linebreak \mbox{the Python argparse module.} 
         \linebreak \mbox{It is available for free download and use on GitHub: \href{https://github.com/Vincenzo1968/myoptParser}{Vincenzo1968/myoptParser}}
         \linebreak \texttt{Python / C}\slashsep\texttt{Bash}\slashsep\texttt{FOSS}\slashsep\texttt{Remote Colab}}

	\entry
		{2006 -- open\\\footnotesize{part time}}
		{Owner}
		{Almalu Trastevere - Cocktail Bar}
		{My family started from scratch a business in entertainment, mainly frequented by English speaking customers. This
gave me, moreover, the opportunity of improving my language skills on a daily basis. This business is still working
and mainly managed by my older brother, Alessio, who is managed by our mother.}
		% {\lorem\lorem\\ \texttt{PHP}\slashsep\texttt{JS}\slashsep\texttt{MariaDB}\slashsep\texttt{Linux}}
	\entry
		{2010 -- 2012} %\\\footnotesize}
		{PHP - MySQL Developer}
		{SirCup}
		{I worked for SirCup, a company which organizes sport
tournaments. I developed and mantained MySQL databases
and relative data handling and presentation PHP routines,
specifically for their soccer tournaments.}
		% {\lorem\lorem\\ \texttt{PHP}\slashsep\texttt{Laravel}}
	\entry
	    { Miscellanea }
	    {}
	    {}
	    {\mbox{After I won a scholarship, I worked for a year as a librarian
in Roma 3 University library.} \linebreak \mbox{I’ve been tutoring students in mathematics and physics for
several years, preparing them for} \linebreak \mbox{any grade level, especially
from high school to univeristy.} \linebreak \mbox{I worked for a couple of years at Chiostro del Bramante, a museum in Roma, keeping watch on} \linebreak \mbox{artworks during exhibitions.}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{}
		{Master's Degree in Mathematical Physics}
		{Universita' Roma Tre}
		{My research work concerns Non-Equilibrium Statistical Mechanics. Specifically,
I focus on the relaxation to equilibrium of metastable thermodynamic systems.
I’m therefore used to implement mathematical models of physical systems, both
stochastic and deterministic.}
	\entry
		{}
		{Bachelor's Degree in Physics}
		{Universita' Roma Tre}
		{Physics}
	\entry
		{}
		{High School}
		{Pio IX}
		{Humanities-focused highschool}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Languages}
	
	\textbf{Italian} - native\\
	\textbf{English} - C1 IELTS Based Result\\
	\textbf{Dutch} - Self Studying
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Hobbies}
	
	I love Art in almost any expression, open air activities when it comes to sport and hicking, cooking \linebreak and reading when home.
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Non profit}
	
	I try to be a better version of me \linebreak every day, working in charities and \linebreak being open mostly. 
\end{minipage}

%----------------------------------------------------------------------------------------
\begin{minipage}[t]{0.5\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
\cvsect{Contacts}

	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
    \qrcode[height=0.3in]{https://github.com/vaeVict1s}                           \quad \icon{Github}{10}{\href{https://github.com/vaeVict1s}{ \small github.com/vaeVict1s}}\\ \\
	\qrcode[height=0.3in]{https://www.linkedin.com/in/leonardo-pozzati-4769471bb} \quad \icon{Linkedin}{10}{\href{https://www.linkedin.com/in/leonardo-pozzati-4769471bb}{ \small in/leonardo-pozzati-4769471bb}}\\ \\
    \qrcode[height=0.3in]{mailto:leon.pozzati@gmail.com}                          \quad \icon{At}{10}{\href{mailto:leon.pozzati@gmail.com}{ \small leon.pozzati@gmail.com}}

\end{minipage}
\hfill
\end{document}
